Supplementary Material for the article \textit{Quotient Normalized Maximum Likelihood Criterion for Learning Bayesian Network Structures}

### 2018-02-15 bn.tex
small edits to make intro fit to one page and to fix the beginning of the section 2.

Bayesian networks are a general way to describe the dependencies
between the components of an $n$\nobreakdash-dimensional discrete data
vector $X=(X_{1},\ldots,X_{n})$ in which the component $X_{i}$ may
take any of the discrete values in a set $\{1,\ldots,r_{i}\}$.
Despite denoting the values with small integers, the model will treat
the components of $X$ as categorical variables.

>>>>

Bayesian networks are a general way to describe the dependencies
between the components of an $n$\nobreakdash-dimensional random data
vector. In this paper we only address the case in which the component
$X_{i}$ of the data vector $X=(X_{1},\ldots,X_{n})$ may take any of
the discrete values in a set $\{1,\ldots,r_{i}\}$.  Despite denoting
the values with small integers, the model will treat each $X_i$
as a categorical variable.

### 2018-02-15 intro.tex
small edits to make intro fit to one page and to fix the beginning of the section 2.

Learning the structure of statistical dependencies can be seen as a
model selection task where each model is a different hypothesis about
the conditional dependencies between sets of variables. Traditional
model selection criteria such as the Akaike information criterion
(AIC)~\cite{Akai73} and the Bayesian information criterion
(BIC)~\cite{Schw78} have also been used for the task, but recent
comparisons have not been favorable for AIC, and BIC appears to
require large sample sizes in order to identify appropriate
structures~\cite{cosco.pgm08a,Liu2012}. Traditionally, the most
popular criterion has been the Bayesian marginal
likelihood~\cite{Heck95b} and its BDeu variant (see
Section~\ref{sec:bns}), but studies~\cite{cosco.uai07,Steck08} have
found this criterion to be very sensitive to hyperparameters and to
yield undesirably complex models for small sample sizes.

>>>>

Learning the structure of statistical dependencies can be seen as a
model selection task where each model is a different hypothesis about
the conditional dependencies between sets of variables. Traditional
model selection criteria such as the Akaike information criterion
(AIC)~\cite{Akai73} and the Bayesian information criterion
(BIC)~\cite{Schw78} have also been used for the task, but recent
comparisons have not been favorable for AIC, and BIC appears to
require large sample sizes in order to identify appropriate
structures~\cite{cosco.pgm08a,Liu2012}. Traditionally, the most
popular criterion has been the Bayesian marginal
likelihood~\cite{Heck95b} and its BDeu variant (see
Section~\ref{sec:bns}), but studies~\cite{cosco.uai07,Steck08} show
this criterion to be sensitive to hyperparameters and to
yield undesirably complex models for small sample sizes.
